### 2024-04-25 appendices/app_EnergyScope.tex
SUBMISSION

% Specific need & criteria

In accordance with the previous classification, models aimed at aiding decision-makers in the energy transition primarily fall under the categories of planning and scenario analysis, with a lower technical resolution than the other classes of model (see Figure \ref{fig:energy_models_classification}). Nonetheless, ensuring technical accuracy is of paramount importance to ensure the effective performance of future energy systems. Hence, these models should meet the following requirements as a minimum:
(i) assessment of intermittent renewable energy integration thanks to an \textbf{hourly resolution} spanning a one-year time horizon;
(ii) accounting for the \textbf{whole-energy system} by including all energy (\ie heat, electricity and mobility) and non-energy flows in different sectors, accounting for their respective greenhouse gas emissions, as well as all resources, conversion processes, and storage technologies;
(iii) exploration of all available options through the \textbf{optimisation of investments and operations};
(iv) consideration of long-term investments throughout the \textbf{transition pathway} process (\ie 30 years up to 2050, in our case); and
(v) ensuring a reasonable \textbf{computational time} (\ie less than one hour on a personal laptop) for analysing different trajectories.
Additionally, to enhance result reproducibility and user understanding, it is advantageous for such models to:
(vi) maintain transparency and preferably be \textbf{open-source}, with accessible data and accompanied by collaborative documentation.

@@

&  {\color{lightgray} \checkmark}\footref{foot:h2res} & \checkmark & \checkmark \\ 

@@

Finally, to properly capture the inter days dynamics, EnergyScope TD uses the ``Coupling typical days'' method from \citet{Gabrielli2018}. Among others, this allows representing the dynamics and the seasonality of storage capacities. This method as well as the clustering approach selected in our case, \ie k-medoids \cite{Kaufman2009,Park2009}, are extensively detailed and compared to other methods, in the work of \citet{limpens2019energyscope}. \\

@@

The proposed formulation relies on representative years, selected every 5 years from 2020 to 2050.  The period between two of them is called `\emph{PHASE}´.
For each of these 7 representative years, the EnergyScope TD model is run  using the relevant data (such as energy demand, technology costs or \gls{GHG} emissions constraints).

@@

\begin{figure}[!htbp]
\centering
\includegraphics[width=\textwidth]{path_e.g._tech.pdf}
\caption{Example of how the technology capacities and associated variables are evolving. The example uses a technology with a 20 years lifetime. Initially 1~GW of capacity exists (\textbf{F\textsubscript{new}} during phase $2015\_2020$). Then another 1~GW is deployed (\textbf{F\textsubscript{new}} during phase $2020\_2025$). 15 years later, a part of the capacity reaches its lifetime limit and is removed (\textbf{F\textsubscript{old}} phase $2035\_2040$). 
Moreover, during the latter phase, additional capacity is decommissioned  prematurely (\textbf{F\textsubscript{decom}}). Finally, the technology reaches its expected lifetime and is fully withdrawn (\textbf{F\textsubscript{old}}).}
\label{fig:path_eg_igcc}
\end{figure}

>>>>

% Specific need & criteria
\newpage
In accordance with the previous classification, models aimed at aiding decision-makers in the energy transition primarily fall under the categories of planning and scenario analysis, with a lower technical resolution than the other classes of model (see Figure \ref{fig:energy_models_classification}). Nonetheless, ensuring technical accuracy is of paramount importance to ensure the effective performance of future energy systems. Hence, these models should meet the following requirements as a minimum:
(i) assessment of intermittent renewable energy integration thanks to an \textbf{hourly resolution} spanning a one-year time horizon;
(ii) accounting for the \textbf{whole-energy system} by including all energy (\ie heat, electricity and mobility) and non-energy flows in different sectors, accounting for their respective greenhouse gas emissions, as well as all resources, conversion processes, and storage technologies;
(iii) exploration of all available options through the \textbf{optimisation of investments and operations};
(iv) consideration of long-term investments throughout the \textbf{transition pathway} process (\ie 30 years up to 2050, in our case); and
(v) ensuring a reasonable \textbf{computational time} (\ie less than one hour on a personal laptop) for analysing different trajectories.
Additionally, to enhance result reproducibility and user understanding, it is advantageous for such models to:
(vi) maintain transparency and preferably be \textbf{open-source}, with accessible data and accompanied by collaborative documentation.

@@

&  {\color{lightgray} \checkmark} & \checkmark & \checkmark \\ 

@@

\newpage
Finally, to properly capture the inter days dynamics, EnergyScope TD uses the ``Coupling typical days'' method from \citet{Gabrielli2018}. Among others, this allows representing the dynamics and the seasonality of storage capacities. This method as well as the clustering approach selected in our case, \ie k-medoids \cite{Kaufman2009,Park2009}, are extensively detailed and compared to other methods, in the work of \citet{limpens2019energyscope}. \\

@@

\newpage
The proposed formulation relies on representative years, selected every 5 years from 2020 to 2050.  The period between two of them is called `\emph{PHASE}´.
For each of these 7 representative years, the EnergyScope TD model is run  using the relevant data (such as energy demand, technology costs or \gls{GHG} emissions constraints).

@@

\begin{figure}[!htbp]
\centering
\includegraphics[width=\textwidth]{path_e.g._tech.pdf}
\caption{Example of how the technology capacities and associated variables are evolving. }
%\caption{Example of how the technology capacities and associated variables are evolving. The example uses a technology with a 20 years lifetime. Initially 1~GW of capacity exists (\textbf{F\textsubscript{new}} during phase $2015\_2020$). Then another 1~GW is deployed (\textbf{F\textsubscript{new}} during phase $2020\_2025$). 15 years later, a part of the capacity reaches its lifetime limit and is removed (\textbf{F\textsubscript{old}} phase $2035\_2040$). Moreover, during the latter phase, additional capacity is decommissioned  prematurely (\textbf{F\textsubscript{decom}}). Finally, the technology reaches its expected lifetime and is fully withdrawn (\textbf{F\textsubscript{old}}).}
\label{fig:path_eg_igcc}
\end{figure}

### 2024-04-25 appendices/app_case_study.tex
SUBMISSION

\section{Myopic versus perfect foresight pathway optimisation}
\label{app:my_vs_pf}
This section aims at digging more into the details of the differences observed between the myopic approaches and the reference case (\ie hourly perfect foresight model).

>>>>

\newpage
\section{Myopic versus perfect foresight pathway optimisation}
\label{app:my_vs_pf}
This section aims at digging more into the details of the differences observed between the myopic approaches and the reference case, the hourly perfect foresight model (see Table \ref{tab:PF_MY}).
